Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-24 Grassmannian_cells.tex
Minor edit

\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$. This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$. 
%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
\end{remark}
%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
%\begin{align}\label{eq:case2}
 %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
%\end{align}
Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$. As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$. Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$

>>>>

\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
Note that the image of the homomorphism corresponding to the basis element spanning $$\Hom(\alpha_{k}^{(-1)}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)$$ corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$. This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma \ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$. 
%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
\end{remark}
%It remains to consider the case when $m$ is even. Lemma \ref{AR} yields
%\begin{align}\label{eq:case2}
 %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
%\end{align}
Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $ \tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $ P_{l}^{[j]}$ for $l\leq m$ and $j=0,\ldots, n-1$ and $l=m+1$ and $j=n-1,\ldots,k$. As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$. Moreover, we define $$\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{(-1)}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.$$
